---
title: "reactonTime"
author: "S4010132"
date: '2023-06-03'
output: html_document
---
TO DO:
- compare rt after being deceived/playing cooperatively

This file contains plots regarding honesty/trust levels and reaction time comparisons


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(dplyr)
library(ggplot2)
library(stringr)
```


Data processing

```{r}
data <- read.csv('game_data.php')
humanData <- data[order(data$game,data$round ),] %>% filter(player!=3) %>% mutate(signal = signal+1, action = action+1) %>% mutate(diff = case_when(
  action-signal <= -2 ~ (action-signal+24),
  action-signal >= -1 ~ (action-signal+0))) 

humanData <- humanData %>% filter(!grepl("(s5_g23|s5_g24)", game))

signals <- humanData %>% filter(round%%2 == player%%2) %>% mutate(honesty = case_when(diff == 0 ~ 1, diff != 0 ~ 0))
responses <- humanData %>% filter(round%%2 != player%%2) %>% mutate(trust = case_when(diff == 1 ~ 1, diff != 1 ~ 0))
honestSignals <- signals %>% filter(honesty == 1)
disHonestSignals <- signals %>% filter(honesty == 0)
trustingResponses <- responses %>% filter(trust == 1)
disTrustingResponses <- responses %>% filter(trust == 0)

block1 <- humanData %>% filter(grepl("(12|34)$", game))
signalsBlock1 <- signals %>% filter(grepl("(12|34)$", game))
responsesBlock1 <- responses %>% filter(grepl("(12|34)$", game))
honestSignalsBlock1 <- honestSignals %>% filter(grepl("(12|34)$", game))
disHonestSignalsBlock1 <- disHonestSignals %>% filter(grepl("(12|34)$", game))
trustingResponsesBlock1 <- trustingResponses %>% filter(grepl("(12|34)$", game))
disTrustingResponsesBlock1 <- disTrustingResponses %>% filter(grepl("(12|34)$", game))

block2 <- humanData %>% filter(grepl("(24|13)$", game))
signalsBlock2 <- signals %>% filter(grepl("(24|13)$", game))
responsesBlock2 <- responses %>% filter(grepl("(24|13)$", game))
honestSignalsBlock2 <- honestSignals %>% filter(grepl("(24|13)$", game))
disHonestSignalsBlock2 <- disHonestSignals %>% filter(grepl("(24|13)$", game))
trustingResponsesBlock2 <- trustingResponses %>% filter(grepl("(24|13)$", game))
disTrustingResponsesBlock2 <- disTrustingResponses %>% filter(grepl("(24|13)$", game))

block3 <- humanData %>% filter(grepl("(14|23)$", game))
signalsBlock3 <- signals %>% filter(grepl("(14|23)$", game))
responsesBlock3 <- responses %>% filter(grepl("(14|23)$", game))
honestSignalsBlock3 <- honestSignals %>% filter(grepl("(14|23)$", game))
disHonestSignalsBlock3 <- disHonestSignals %>% filter(grepl("(14|23)$", game))
trustingResponsesBlock3 <- trustingResponses %>% filter(grepl("(14|23)$", game))
disTrustingResponsesBlock3 <- disTrustingResponses %>% filter(grepl("(14|23)$", game))
```

Boxplots reaction time of playing honestly/dishonestly after signalling over all blocks and for each block
```{r pressure, echo=FALSE}

# all blocks
boxplot(log(honestSignals$reactionTime), log(disHonestSignals$reactionTime),
        main = "Logarithm of reaction times per participant after signalling 
over all blocks",
        at = c(1,2),
        names = c("HRT", "DRT"),
        las = 2,
        col = c("grey","grey"),
        border = "black",
        horizontal = FALSE,
        notch = FALSE,
        ylab = "Log of reaction times (s)",
        cex.lab = 1
)
# 
# # block 1
# boxplot(log(honestSignalsBlock1$reactionTime), log(disHonestSignalsBlock1$reactionTime),
#         main = "Logarithm of reaction times per participant after signalling 
# for block 1",
#         at = c(1,2),
#         names = c("HRT", "DRT"),
#         las = 2,
#         col = c("grey","grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "Log of reaction times (s)",
#         cex.lab = 1
# )
# 
# #block 2
# boxplot(log(honestSignalsBlock2$reactionTime), log(disHonestSignalsBlock2$reactionTime),
#         main = "Logarithm of reaction times per participant after signalling 
# for block 2",
#         at = c(1,2),
#         names = c("HRT", "DRT"),
#         las = 2,
#         col = c("grey","grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "Log of reaction times (s)",
#         cex.lab = 1
# )
# 
# #block 3
# boxplot(log(honestSignalsBlock3$reactionTime), log(disHonestSignalsBlock3$reactionTime),
#         main = "Logarithm of reaction times per participant after signalling 
# for block 3",
#         at = c(1,2),
#         names = c("HRT", "DRT"),
#         las = 2,
#         col = c("grey","grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "Log of reaction times (s)",
#         cex.lab = 1
# )
```

Boxplots reaction time of playing trusting/distrusting after receiving a signal over all blocks and for each block
```{r}
# all blocks
boxplot(log(trustingResponses$reactionTime), log(disTrustingResponses$reactionTime),
        main = "Logarithm of reaction times per participant after receiving signal 
over all blocks",
        at = c(1,2),
        names = c("TRT", "DRT"),
        las = 2,
        col = c("grey","grey"),
        border = "black",
        horizontal = FALSE,
        notch = FALSE,
        ylab = "Log of reaction times (s)",
        cex.lab = 1
)

# # block 1
# boxplot(log(trustingResponsesBlock1$reactionTime), log(disTrustingResponsesBlock1$reactionTime),
#         main = "Logarithm of reaction times per participant after receiving signal 
# for block 1",
#         at = c(1,2),
#         names = c("TRT", "DRT"),
#         las = 2,
#         col = c("grey","grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "Log of reaction times (s)",
#         cex.lab = 1
# )

# #block 2
# boxplot(log(trustingResponsesBlock2$reactionTime), log(disTrustingResponsesBlock2$reactionTime),
#         main = "Logarithm of reaction times per participant after receiving signal 
# for block 2",
#         at = c(1,2),
#         names = c("TRT", "DRT"),
#         las = 2,
#         col = c("grey","grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "Log of reaction times (s)",
#         cex.lab = 1
# )

# #block 3
# boxplot(log(trustingResponsesBlock3$reactionTime), log(disTrustingResponsesBlock3$reactionTime),
#         main = "Logarithm of reaction times per participant after receiving signal 
# for block 3",
#         at = c(1,2),
#         names = c("TRT", "DRT"),
#         las = 2,
#         col = c("grey","grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "Log of reaction times (s)",
#         cex.lab = 1
# )
```

data split human human / human agent
```{r}
signalsHH <- signals %>% filter(!grepl("4$", game))
signalsHA <- signals %>% filter(grepl("4$", game))

signalsBlock1HH <- signalsBlock1 %>% filter(!grepl("4$", game))
signalsBlock1HA <- signalsBlock1 %>% filter(grepl("4$", game))

signalsBlock2HH <- signalsBlock2 %>% filter(!grepl("4$", game))
signalsBlock2HA <- signalsBlock2 %>% filter(grepl("4$", game))

signalsBlock3HH <- signalsBlock3 %>% filter(!grepl("4$", game))
signalsBlock3HA <- signalsBlock3 %>% filter(grepl("4$", game))

responsesHH <- responses %>% filter(!grepl("4$", game))
responsesHA <- responses %>% filter(grepl("4$", game))

responsesBlock1HH <- responsesBlock1 %>% filter(!grepl("4$", game))
responsesBlock1HA <- responsesBlock1 %>% filter(grepl("4$", game))

responsesBlock2HH <- responsesBlock2 %>% filter(!grepl("4$", game))
responsesBlock2HA <- responsesBlock2 %>% filter(grepl("4$", game))

responsesBlock3HH <- responsesBlock3 %>% filter(!grepl("4$", game))
responsesBlock3HA <- responsesBlock3 %>% filter(grepl("4$", game))
```

Boxplots reaction time of playing: human vs human and human vs agent after signalling and after receiving signal all blocks
```{r}
# signaler human/agent reaction time all blocks
boxplot(log(signalsHH$reactionTime), log(signalsHA$reactionTime),
        main = "Logarithm of reaction times per participant 
        after signalling",
        at = c(1,2),
        names = c("Human", "Agent"),
        las = 2,
        col = c("grey","grey"),
        border = "black",
        horizontal = FALSE,
        notch = FALSE,
        ylab = "Log of reaction times (s)",
        cex.lab = 1
)

# responder human/agent reaction time all blocks
boxplot(log(responsesHH$reactionTime), log(responsesHA$reactionTime),
        main = "Logarithm of reaction times per participant 
        after receiving signal",
        at = c(1,2),
        names = c("Human", "Agent"),
        las = 2,
        col = c("grey","grey"),
        border = "black",
        horizontal = FALSE,
        notch = FALSE,
        ylab = "Log of reaction times (s)",
        cex.lab = 1
)
```
data split human/agent conditions
```{r}
signalsListHH <- group_split(signalsHH, signalsHH$game)
signalsListHA <- group_split(signalsHA, signalsHA$game)

signalsListBlock1HH <- group_split(signalsBlock1HH, signalsBlock1HH$game)
signalsListBlock1HA <- group_split(signalsBlock1HA, signalsBlock1HA$game)

signalsListBlock2HH <- group_split(signalsBlock2HH, signalsBlock2HH$game)
signalsListBlock2HA <- group_split(signalsBlock2HA, signalsBlock2HA$game)

signalsListBlock3HH <- group_split(signalsBlock3HH, signalsBlock3HH$game)
signalsListBlock3HA <- group_split(signalsBlock3HA, signalsBlock3HA$game)

responsesListHH <- group_split(responsesHH, responsesHH$game)
responsesListHA <- group_split(responsesHA, responsesHA$game)

responsesListBlock1HH <- group_split(responsesBlock1HH, responsesBlock1HH$game)
responsesListBlock1HA <- group_split(responsesBlock1HA, responsesBlock1HA$game)

responsesListBlock2HH <- group_split(responsesBlock2HH, responsesBlock2HH$game)
responsesListBlock2HA <- group_split(responsesBlock2HA, responsesBlock2HA$game)

responsesListBlock3HH <- group_split(responsesBlock3HH, responsesBlock3HH$game)
responsesListBlock3HA <- group_split(responsesBlock3HA, responsesBlock3HA$game)
```

honesty levels human/agent condition, for all blocks and each block
```{r}

honestyVector <- c()
honestyGames <- c()

honestyVectorHH <- c()
honestyGamesHH <- c()
honestyVectorBlock1HH <- c()
honestyGamesBlock1HH <- c()
honestyVectorBlock2HH <- c()
honestyGamesBlock2HH <- c()
honestyVectorBlock3HH <- c()
honestyGamesBlock3HH <- c()

for (game in signalsListHH){
  honestySumHH = sum(game$honesty)/20*100
  honestyVector <- c(honestyVector, honestySumHH)
  honestyVectorHH <- c(honestyVectorHH, honestySumHH)
  honestyGamesHH <- c(honestyGamesHH, head(game$game, 1))
  honestyGames <- c(honestyGames, head(game$game, 1))
  if(grepl("12$", head(game$game, 1))){
      honestyVectorBlock1HH <- c(honestyVectorBlock1HH, honestySumHH)
      honestyGamesBlock1HH <- c(honestyGamesBlock1HH, head(game$game, 1))
  }else if(grepl("13$", head(game$game, 1))){
      honestyVectorBlock2HH <- c(honestyVectorBlock2HH, honestySumHH)
      honestyGamesBlock2HH <- c(honestyGamesBlock2HH, head(game$game, 1))
  } else {
      honestyVectorBlock3HH <- c(honestyVectorBlock3HH, honestySumHH)
      honestyGamesBlock3HH <- c(honestyGamesBlock3HH, head(game$game, 1))
  }
}
honestyFrameHH = data.frame(honestyVectorHH, honestyGamesHH)
honestyFrameBlock1HH = data.frame(honestyVectorBlock1HH, honestyGamesBlock1HH)
honestyFrameBlock2HH = data.frame(honestyVectorBlock2HH, honestyGamesBlock2HH)
honestyFrameBlock3HH = data.frame(honestyVectorBlock3HH, honestyGamesBlock3HH)


honestyVectorHA <- c()
honestyGamesHA <- c()
honestyVectorBlock1HA <- c()
honestyGamesBlock1HA <- c()
honestyVectorBlock2HA <- c()
honestyGamesBlock2HA <- c()
honestyVectorBlock3HA <- c()
honestyGamesBlock3HA <- c()

for (game in signalsListHA){
  honestySumHA = sum(game$honesty)/10*100
  honestyVector <- c(honestyVector, honestySumHA)
  honestyVectorHA <- c(honestyVectorHA, honestySumHA)
  honestyGamesHA <- c(honestyGamesHA, head(game$game, 1))
  honestyGames <- c(honestyGames, head(game$game, 1))
  if(grepl("34$", head(game$game, 1))){
      honestyVectorBlock1HA <- c(honestyVectorBlock1HA, honestySumHA)
      honestyGamesBlock1HA <- c(honestyGamesBlock1HA, head(game$game, 1))
  }else if(grepl("24$", head(game$game, 1))){
      honestyVectorBlock2HA <- c(honestyVectorBlock2HA, honestySumHA)
      honestyGamesBlock2HA <- c(honestyGamesBlock2HA, head(game$game, 1))
  } else {
      honestyVectorBlock3HA <- c(honestyVectorBlock3HA, honestySumHA)
      honestyGamesBlock3HA <- c(honestyGamesBlock3HA, head(game$game, 1))
  }
}
honestyFrameHA = data.frame(honestyVectorHA, honestyGamesHA)
honestyFrameBlock1HA = data.frame(honestyVectorBlock1HA, honestyGamesBlock1HA)
honestyFrameBlock2HA = data.frame(honestyVectorBlock2HA, honestyGamesBlock2HA)
honestyFrameBlock3HA = data.frame(honestyVectorBlock3HA, honestyGamesBlock3HA)

honestyFrame = data.frame(honestyVector, honestyGames)


# all blocks
boxplot(honestyFrameHH$honestyVectorHH, honestyFrameHA$honestyVectorHA,
        main = "honesty levels human/agent all blocks",
        at = c(1,2),
        names = c("HH", "HA"),
        las = 2,
        col = c("grey", "grey", "grey", "grey", "grey"),
        border = "black",
        horizontal = FALSE,
        notch = FALSE,
        ylab = "honesty level (%)",
        ylim = c(0, 100)
)

# # block 1
# boxplot(honestyFrameBlock1HH$honestyVectorBlock1HH, honestyFrameBlock1HA$honestyVectorBlock1HA,
#         main = "honesty levels human/agent block 1",
#         at = c(1,2),
#         names = c("HH", "HA"),
#         las = 2,
#         col = c("grey", "grey", "grey", "grey", "grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "honesty levels (%)",
#         ylim = c(0, 100)
# )
# 
# # block 2
# boxplot(honestyFrameBlock2HH$honestyVectorBlock2HH, honestyFrameBlock2HA$honestyVectorBlock2HA,
#         main = "honesty levels human/agent block 2",
#         at = c(1,2),
#         names = c("HH", "HA"),
#         las = 2,
#         col = c("grey", "grey", "grey", "grey", "grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "honesty levels (%)",
#         ylim = c(0, 100)
# )
# 
# # block 3
# boxplot(honestyFrameBlock3HH$honestyVectorBlock3HH, honestyFrameBlock3HA$honestyVectorBlock3HA,
#         main = "honesty levels human/agent block 3",
#         at = c(1,2),
#         names = c("HH", "HA"),
#         las = 2,
#         col = c("grey", "grey", "grey", "grey", "grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "honesty levels (%)",
#         ylim = c(0, 100)
# )

```

trust levels human/agent condition, for all blocks and each block

```{r}

trustVector <- c()
trustGames <- c()

trustVectorHH <- c()
trustGamesHH <- c()
trustVectorBlock1HH <- c()
trustGamesBlock1HH <- c()
trustVectorBlock2HH <- c()
trustGamesBlock2HH <- c()
trustVectorBlock3HH <- c()
trustGamesBlock3HH <- c()

for (game in responsesListHH){
  print(sum(game$trust))
  trustSumHH = sum(game$trust)/20*100
  trustVector <- c(trustVector, trustSumHH)
  trustVectorHH <- c(trustVectorHH, trustSumHH)
  trustGames <- c(trustGames, head(game$game, 1))
  trustGamesHH <- c(trustGamesHH, head(game$game, 1))
  if(grepl("12$", head(game$game, 1))){
      trustVectorBlock1HH <- c(trustVectorBlock1HH, trustSumHH)
      trustGamesBlock1HH <- c(trustGamesBlock1HH, head(game$game, 1))
  }else if(grepl("13$", head(game$game, 1))){
      trustVectorBlock2HH <- c(trustVectorBlock2HH, trustSumHH)
      trustGamesBlock2HH <- c(trustGamesBlock2HH, head(game$game, 1))
  } else {
      trustVectorBlock3HH <- c(trustVectorBlock3HH, trustSumHH)
      trustGamesBlock3HH <- c(trustGamesBlock3HH, head(game$game, 1))
  }
}
trustFrameHH = data.frame(trustVectorHH, trustGamesHH)
trustFrameBlock1HH = data.frame(trustVectorBlock1HH, trustGamesBlock1HH)
trustFrameBlock2HH = data.frame(trustVectorBlock2HH, trustGamesBlock2HH)
trustFrameBlock3HH = data.frame(trustVectorBlock3HH, trustGamesBlock3HH)


trustVectorHA <- c()
trustGamesHA <- c()
trustVectorBlock1HA <- c()
trustGamesBlock1HA <- c()
trustVectorBlock2HA <- c()
trustGamesBlock2HA <- c()
trustVectorBlock3HA <- c()
trustGamesBlock3HA <- c()

for (game in responsesListHA){
  trustSumHA = sum(game$trust)/10*100
  trustVector <- c(trustVector, trustSumHA)
  trustVectorHA <- c(trustVectorHA, trustSumHA)
  trustGames <- c(trustGames, head(game$game, 1))
  trustGamesHA <- c(trustGamesHA, head(game$game, 1))
  if(grepl("34$", head(game$game, 1))){
      trustVectorBlock1HA <- c(trustVectorBlock1HA, trustSumHA)
      trustGamesBlock1HA <- c(trustGamesBlock1HA, head(game$game, 1))
  }else if(grepl("24$", head(game$game, 1))){
      trustVectorBlock2HA <- c(trustVectorBlock2HA, trustSumHA)
      trustGamesBlock2HA <- c(trustGamesBlock2HA, head(game$game, 1))
  } else {
      trustVectorBlock3HA <- c(trustVectorBlock3HA, trustSumHA)
      trustGamesBlock3HA <- c(trustGamesBlock3HA, head(game$game, 1))
  }
}
trustFrameHA = data.frame(trustVectorHA, trustGamesHA)
trustFrameBlock1HA = data.frame(trustVectorBlock1HA, trustGamesBlock1HA)
trustFrameBlock2HA = data.frame(trustVectorBlock2HA, trustGamesBlock2HA)
trustFrameBlock3HA = data.frame(trustVectorBlock3HA, trustGamesBlock3HA)

trustFrame = data.frame(trustVector, trustGames)


# all blocks
boxplot(trustFrameHH$trustVectorHH, trustFrameHA$trustVectorHA,
        main = "trust levels human/agent all blocks",
        at = c(1,2),
        names = c("HH", "HA"),
        las = 2,
        col = c("grey", "grey", "grey", "grey", "grey"),
        border = "black",
        horizontal = FALSE,
        notch = FALSE,
        ylab = "trust levels (%)",
        ylim = c(0, 100)
)

# # block 1
# boxplot(trustFrameBlock1HH$trustVectorBlock1HH, trustFrameBlock1HA$trustVectorBlock1HA,
#         main = "trust levels human/agent block 1",
#         at = c(1,2),
#         names = c("HH", "HA"),
#         las = 2,
#         col = c("grey", "grey", "grey", "grey", "grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "trust levels (%)",
#         ylim = c(0, 100)
# )
# 
# # block 2
# boxplot(trustFrameBlock2HH$trustVectorBlock2HH, trustFrameBlock2HA$trustVectorBlock2HA,
#         main = "trust levels human/agent block 2",
#         at = c(1,2),
#         names = c("HH", "HA"),
#         las = 2,
#         col = c("grey", "grey", "grey", "grey", "grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "trust levels (%)",
#         ylim = c(0, 100)
# )
# 
# # block 3
# boxplot(trustFrameBlock3HH$trustVectorBlock3HH, trustFrameBlock3HA$trustVectorBlock3HA,
#         main = "trust levels human/agent block 3",
#         at = c(1,2),
#         names = c("HH", "HA"),
#         las = 2,
#         col = c("grey", "grey", "grey", "grey", "grey"),
#         border = "black",
#         horizontal = FALSE,
#         notch = FALSE,
#         ylab = "trust levels (%)",
#         ylim = c(0, 100)
# )

```

